### 2015-03-25 Paper1Editted/paper1Beditted.tex
Updated to cite khalil

To explore the conditions under which this procedure for recovering the intent trajectory can be generalized, we must take a series of counter-intuitive steps. First, we distinguish between joint space and generalized space by introducing a generalized state variable, $x$. Second, we separate the plant (arm) into its process (dynamics), $P$, and actuator (muscles), $A$, components. Third, we use power series expansions to model these components in a very general sense,
\begin{equation} \label{eq:generalPlant}
\underbrace{\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+\overbrace{\sum_{m=1}^M A_m(x-x_e)^{(m)}}^\text{Actuator}}_\text{Plant}+E=0
\end{equation}
where $x_e$ is the equilibrium trajectory of the actuator. Fourth, we describe the actuator control law using the same expansions,
\begin{equation}
\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m(x_d-x_e)^{(m)}}^\text{Actuator}=0
\end{equation}
where an internal model, $\hat{P}$ and $\hat{E}$, predicts system dynamics and external disturbances in order to determine the actuator equilibrium $x_e$ such that $x$ will track a desired path $x_d$. The feedforward component must use the actuator and hence it shares the actuator's equilibrium with the plant. This allows us to finally relate the physical system and its control law by solving for $x_e$ and substituting into \eqref{eq:generalPlant},
\begin{equation}
\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+E=\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m (x_d-x)^{(m)}}^\text{Feedback (Actuator)}
\end{equation}
wherein $x_e$ vanishes recovering our familiar model. While a proper choice of $x_e$ is perhaps essential for control, our approach does not require a model relating this equilibrium and intended trajectory. Note also that the actuator's equilibrium $x_e$ is not the process's equilibrium unless all derivatives of $x_d$ are zero. This is important as the actuator state ($\lambda$) has been claimed to be the intended movement\cite{feldman1995origin}. This upholds Gomi and Kawato's finding that the arm muscles' equilibrium does not represent reaching intent\cite{gomi1997human}. If the highest order coefficient of the dynamic model of the process $\hat{P}_N$ can be inverted and the impedances can be modeled, it is possible to solve for $x_d^{(N)}$ and integrate for $x_d$ revealing the intended trajectory.

While we treat both the process and actuator as dynamic models in our derivation, it is important to note that both the derivation and the technique are agnostic to the process model. Instead of a dynamic model, it could be a lookup table. For instance, a switch is well-modeled as a lookup table or threshold without any consideration of its underlying mechanism. In this case, our technique could be used to determine a person's intention to flip the switch and how it changes in the face of disturbance. As long as some bidirectional relationship exists between state and outcome (even if determined empirically), intended outcome can be determined. This allows determination of intent in many situations of interest, even where the process is irreducibly complex.

@@

It is important to mention that it is not necessary for the brain to represent intent explicitly to generate action. It is possible that the nervous system can simply learn the relationship between muscle activations and the accomplishment of goals. For example, one might simply evaluate a motion outcome and adjust descending signals to the muscles. At the same time, one may not deny the fact that there are tasks that require a explicit representation of a trajectory, such as performing a dance, drawing a picture, or conducting an orchestra. For these tasks, intent is likely represented at  some level in the nervous system. Nevertheless, the mechanics of the arm dictate the existence of an equilibrium whether intent is explicitly represented or not. Here our goal was more modest, which was to answer, ``where would the arm have gone?''

>>>>

To explore the conditions under which this procedure for recovering the intent trajectory can be generalized, we must take a series of counter-intuitive steps. First, we distinguish between joint space and generalized space by introducing a generalized state variable, $x$. Second, we separate the plant (arm) into its process (dynamics), $P$, and actuator (muscles), $A$, components. Third, we model these components in a very general sense as time-varying linear systems,
\begin{equation} \label{eq:generalPlant}
\underbrace{\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+\overbrace{\sum_{m=1}^M A_m(x-x_e)^{(m)}}^\text{Actuator}}_\text{Plant}+E=0
\end{equation}
where $x_e$ is the equilibrium trajectory of the actuator. Linearization is informative here because stable equilibrium points of linearizations of nonlinear systems are also equilibrium points of the nonlinear system\cite[p.~156]{khalil2002nonlinear} as long as the Jacobian is bounded and Lipschitz continuous\cite[p.~161]{khalil2002nonlinear}. Fourth, we describe the actuator control law using the same expansions,
\begin{equation}
\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m(x_d-x_e)^{(m)}}^\text{Actuator}=0
\end{equation}
where an internal model, $\hat{P}$ and $\hat{E}$, predicts system dynamics and external disturbances in order to determine the actuator equilibrium $x_e$ such that $x$ will track a desired path $x_d$. The feedforward component must use the actuator and hence it shares the actuator's equilibrium with the plant. This allows us to finally relate the physical system and its control law by solving for $x_e$ and substituting into \eqref{eq:generalPlant},
\begin{equation}
\overbrace{\sum_{n=1}^N P_nx^{(n)}}^\text{Process}+E=\overbrace{\sum_{n=1}^N \hat{P}_n x^{(n)}_d+\hat{E}}^\text{Internal Model}+\overbrace{\sum_{m=1}^M A_m (x_d-x)^{(m)}}^\text{Feedback (Actuator)}
\end{equation}
wherein $x_e$ vanishes recovering our familiar model. While a proper choice of $x_e$ is perhaps essential for control, our approach does not require a model relating this equilibrium and intended trajectory. Note also that the actuator's equilibrium $x_e$ is not the process's equilibrium unless all derivatives of $x_d$ are zero. This is important as the actuator state ($\lambda$) has been claimed to be the intended movement\cite{feldman1995origin}. This upholds Gomi and Kawato's finding that the arm muscles' equilibrium does not represent reaching intent\cite{gomi1997human}. If the highest order coefficient of the dynamic model of the process $\hat{P}_N$ can be inverted, the impedances can be modeled, and the linearized system is stable, it is possible to solve for $x_d^{(N)}$ and integrate for $x_d$ revealing the intended trajectory.

While we treat both the process and actuator as dynamic models in our derivation, it is important to note that both the derivation and the technique are agnostic to the process model so long as its input is a stable equilbrium. Instead of a dynamic model, it could be a lookup table. For instance, a switch is well-modeled as a lookup table or threshold without any consideration of its underlying mechanism. In this case, our technique could be used to determine a person's intention to flip the switch and how it changes in the face of disturbance. As long as some bidirectional relationship exists between state and outcome (even if determined empirically), intended outcome can be determined. This allows determination of intent in many situations of interest, even where the process is otherwise irreducibly complex.

@@

It is important to mention that it is not necessary for the brain to represent intent explicitly to generate action. It is possible that the nervous system can simply learn the relationship between muscle activations and the accomplishment of goals. For example, one might simply evaluate a motion outcome and adjust descending signals to the muscles. At the same time, one may not deny the fact that there are tasks that require a explicit representation of a trajectory, such as performing a dance, drawing a picture, or conducting an orchestra. For these tasks, intent is likely represented at  some level in the nervous system. Nevertheless, the mechanics of the arm dictate the existence of an equilibrium whether intent is explicitly represented or not. Here our goal was to answer a more modest question, ``where would the arm have gone?''
